### 2022-07-16 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@afdc65f85795a7aa4e4a02aef00617b266eb78be 🚀

We acknowledge that this study was conducted on land within the
traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. GH,
FB, GD, and NF are funded by the NSERC Computational Biodiversity
Science and Services (BIOS\(^2\)) CREATE program; FB, NF, and TP are
funded by the Institute for Data Valorization (IVADO); NF and TP are
funded by a donation from the Courtois Foundation; GD is funded by the
Natural Sciences and Engineering Research Council (NSERC) and the Fond
de recherche du Québec - Nature et technologie (FRQNT) doctoral
scholarships; TP is funded by the Canadian Institute of Ecology \&
Evolution; FW is funded by the Royal Society (Grant number:
CHL\textbackslash R1\textbackslash180156). We thank the editor and
reviewer for their thoughtful comments, which considerably improved this
manuscript.

@@

\leavevmode\hypertarget{ref-Dallas2020AbuNot}{}%
Dallas, Tad, Samuel Pironon, and Luca Santini. 2020. {``The
Abundant-Centre Is Not All That Abundant: A Comment to Osorio-Olvera Et
Al. 2020,''} May, 2020.02.27.968586.
\url{https://doi.org/10.1101/2020.02.27.968586}.

@@

\leavevmode\hypertarget{ref-Dansereau2021SimJl}{}%
---------. 2021. {``SimpleSDMLayers.jl and GBIF.jl: A Framework for
Species Distribution Modeling in Julia.''} \emph{Journal of Open Source
Software} 6 (57): 2872. \url{https://doi.org/10.21105/joss.02872}.

\leavevmode\hypertarget{ref-Daru2020GreToo}{}%
Daru, Barnabas H. 2020. {``GreenMaps: A Tool for Addressing the
Wallacean Shortfall in the Global Distribution of Plants.''}
\emph{bioRxiv}, February, 2020.02.21.960161.
\url{https://doi.org/10.1101/2020.02.21.960161}.

@@

\leavevmode\hypertarget{ref-Ficetola2014EvaRoba}{}%
Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
Katariya, Emilio Padoa-Schioppa, and Ariadne Angulo. 2014. {``An
Evaluation of the Robustness of Global Amphibian Range Maps.''}
\emph{Journal of Biogeography} 41 (2): 211--21.
\url{https://doi.org/10.1111/jbi.12206}.

\leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
Fourcade, Yoan. 2016. {``Comparing Species Distributions Modelled from
Occurrence Data and from Expert-Based Range Maps. Implication for
Predicting Range Shifts with Climate Change.''} \emph{Ecological
Informatics} 36 (November): 8--14.
\url{https://doi.org/10.1016/j.ecoinf.2016.09.002}.

\leavevmode\hypertarget{ref-Fricke2022EffDef}{}%
Fricke, Evan C., Alejandro Ordonez, Haldre S. Rogers, and Jens-Christian
Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
Track Climate Change.''} \emph{Science}, January.
\url{https://doi.org/10.1126/science.abk3510}.

@@

\leavevmode\hypertarget{ref-Poisot2020EnvBia}{}%
Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
Dominique Gravel, Andrew Macdonald, Benjamin Mercier, Clément Violet,
and Steve Vissault. 2020. {``Environmental Biases in the Study of
Ecological Networks at the Planetary Scale.''} \emph{bioRxiv}, January,
2020.01.27.921429. \url{https://doi.org/10.1101/2020.01.27.921429}.

@@

\leavevmode\hypertarget{ref-Ronquillo2020AssSpa}{}%
Ronquillo, Cristina, Fernanda Alves-Martins, Vicente Mazimpaka, Thadeu
Sobral-Souza, Bruno Vilela-Silva, Nagore G. Medina, and Joaquín Hortal.
2020. {``Assessing Spatial and Temporal Biases and Gaps in the Publicly
Available Distributional Information of Iberian Mosses.''}
\emph{Biodiversity Data Journal} 8 (September): e53474.
\url{https://doi.org/10.3897/BDJ.8.e53474}.

@@

\leavevmode\hypertarget{ref-Scott2018RolHer}{}%
Scott, Abigail L., Paul H. York, Clare Duncan, Peter I. Macreadie, Rod
M. Connolly, Megan T. Ellis, Jessie C. Jarvis, Kristin I. Jinks, Helene
Marsh, and Michael A. Rasheed. 2018. {``The Role of Herbivory in
Structuring Tropical Seagrass Ecosystem Service Delivery.''}
\emph{Frontiers in Plant Science} 9 (February): 127.
\url{https://doi.org/10.3389/fpls.2018.00127}.

@@

\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLosa}{}%
Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan
Arroyo, Andrea Cocucci, Mauro Galetti, María B. García, et al. 2015.
{``Beyond Species Loss: The Extinction of Ecological Interactions in a
Changing World.''} Edited by Marc Johnson. \emph{Functional Ecology} 29
(3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.

@@

\leavevmode\hypertarget{ref-Windsor2022UsiEco}{}%
---------. 2022. {``Using Ecological Networks to Answer Questions in
Global Biogeography and Ecology.''} \emph{Journal of Biogeography} n/a
(n/a). \url{https://doi.org/10.1111/jbi.14447}.

>>>>

We acknowledge that this study was conducted on land within the
traditional unceded territory of the Saint Lawrence Iroquoian,
Anishinabewaki, Mohawk, Huron-Wendat, and Omàmiwininiwak nations. We
thank the editor and reviewer for their thoughtful comments, which
considerably improved this manuscript.

@@

\leavevmode\hypertarget{ref-Dallas2020AbuNot}{}%
Dallas, Tad, Samuel Pironon, and Luca Santini. 2020. {``The
Abundant-Centre Is Not All That Abundant: A Comment to Osorio-Olvera Et
Al. 2020,''} 2020.02.27.968586.
\url{https://doi.org/10.1101/2020.02.27.968586}.

@@

\leavevmode\hypertarget{ref-Daru2020GreToo}{}%
Daru, Barnabas H. 2020. {``GreenMaps: A Tool for Addressing the
Wallacean Shortfall in the Global Distribution of Plants.''}
\emph{bioRxiv}, 2020.02.21.960161.
\url{https://doi.org/10.1101/2020.02.21.960161}.

@@

\leavevmode\hypertarget{ref-Ficetola2014EvaRob}{}%
Ficetola, Gentile Francesco, Carlo Rondinini, Anna Bonardi, Vineet
Katariya, Emilio Padoa-Schioppa, and Ariadne Angulo. 2014. {``An
Evaluation of the Robustness of Global Amphibian Range Maps.''}
\emph{Journal of Biogeography} 41 (2): 211--21.
\url{https://doi.org/10.1111/jbi.12206}.

\leavevmode\hypertarget{ref-Fourcade2016ComSpe}{}%
Fourcade, Yoan. 2016. {``Comparing Species Distributions Modelled from
Occurrence Data and from Expert-Based Range Maps. Implication for
Predicting Range Shifts with Climate Change.''} \emph{Ecological
Informatics} 36: 8--14.
\url{https://doi.org/10.1016/j.ecoinf.2016.09.002}.

\leavevmode\hypertarget{ref-Fricke2022EffDef}{}%
Fricke, Evan C., Alejandro Ordonez, Haldre S. Rogers, and Jens-Christian
Svenning. 2022. {``The Effects of Defaunation on Plants' Capacity to
Track Climate Change.''} \emph{Science}.
\url{https://doi.org/10.1126/science.abk3510}.

@@

\leavevmode\hypertarget{ref-Poisot2020EnvBia}{}%
Poisot, Timothée, Gabriel Bergeron, Kevin Cazelles, Tad Dallas,
Dominique Gravel, Andrew Macdonald, Benjamin Mercier, Clément Violet,
and Steve Vissault. 2020. {``Environmental Biases in the Study of
Ecological Networks at the Planetary Scale.''} \emph{bioRxiv},
2020.01.27.921429. \url{https://doi.org/10.1101/2020.01.27.921429}.

@@

\leavevmode\hypertarget{ref-Ronquillo2020AssSpa}{}%
Ronquillo, Cristina, Fernanda Alves-Martins, Vicente Mazimpaka, Thadeu
Sobral-Souza, Bruno Vilela-Silva, Nagore G. Medina, and Joaquín Hortal.
2020. {``Assessing Spatial and Temporal Biases and Gaps in the Publicly
Available Distributional Information of Iberian Mosses.''}
\emph{Biodiversity Data Journal} 8: e53474.
\url{https://doi.org/10.3897/BDJ.8.e53474}.

@@

\leavevmode\hypertarget{ref-Scott2018RolHer}{}%
Scott, Abigail L., Paul H. York, Clare Duncan, Peter I. Macreadie, Rod
M. Connolly, Megan T. Ellis, Jessie C. Jarvis, Kristin I. Jinks, Helene
Marsh, and Michael A. Rasheed. 2018. {``The Role of Herbivory in
Structuring Tropical Seagrass Ecosystem Service Delivery.''}
\emph{Frontiers in Plant Science} 9: 127.
\url{https://doi.org/10.3389/fpls.2018.00127}.

@@

\leavevmode\hypertarget{ref-Valiente-Banuet2015SpeLos}{}%
Valiente-Banuet, Alfonso, Marcelo A. Aizen, Julio M. Alcántara, Juan
Arroyo, Andrea Cocucci, Mauro Galetti, María B. García, et al. 2015.
{``Beyond Species Loss: The Extinction of Ecological Interactions in a
Changing World.''} Edited by Marc Johnson. \emph{Functional Ecology} 29
(3): 299--307. \url{https://doi.org/10.1111/1365-2435.12356}.

@@
